
%-------------------------
% Resume in LaTeX
% Author: Azizzhan Supiyev (adapted from Jake's Resume template)
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\hypersetup{
  colorlinks=true,      % paint the text (instead of putting boxes)
  urlcolor=NavyBlue,    % colour for \href and URLs
  linkcolor=NavyBlue,   % internal links (section refs, etc.)
  citecolor=NavyBlue    % bibliography links
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.08003pt}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Azizzhan Supiyev} \\ \vspace{1pt}
    \small Software Engineer \\
    \href{mailto:azeasy19@gmail.com}{azeasy19@gmail.com} $|$
    \href{https://linkedin.com/in/azeasy}{LinkedIn} $|$
    \href{https://github.com/azeasy}{GitHub} $|$
    Telegram: \href{https://t.me/azeasy}{@azeasy}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Experienced Software Engineer specializing in \textbf{Python/Django}, REST APIs, and scalable architectures. Proven at integrating complex systems (OpenAI, Google, LinkedIn, Gekata APIs), designing data pipelines, and applying strong mathematical reasoning to deliver robust solutions.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Akhter Studios}{Nov 2023 -- Feb 2026}
{Software Engineer}{Almaty, KZ}
\resumeItemListStart
    \resumeItem{\textbf{Introdex}: Integrated Google, LinkedIn, and other APIs; optimized search by normalizing and indexing legacy database, search speed went down from 5-7 second to under 300ms.}
    \resumeItem{\textbf{MyStudy}: Developed educational platform and AI‑powered test generation engine, optimized prompts to the low-cost model to reduce hallucinations and increase accuracy.}
    \resumeItem{\textbf{AI Vendor Discovery Agent}: Engineered a Django-based chatbot using Llama 3 with custom tool-calling capabilities to automate vendor matching and complex database queries via Telegram or WhatsApp.}
    \resumeItem{Tech: Django, DRF, Asyncio, Celery, PostgreSQL, Redis, Docker, Pytest, FastAPI, LangChain, LangGraph, LLMs (OpenAI, xAI, LLama)}
\resumeItemListEnd

\resumeSubheading
{Adal-Meteo}{Jan 2020 -- Oct 2023}
{Software Engineer}{Almaty, KZ}
\resumeItemListStart
    \resumeItem{Built REST APIs, ETL pipelines, and real‑time dashboards for ecological monitoring.}
    \resumeItem{Implemented an ETL service with visual dashboards for forecasting systems comparison.}
    \resumeItem{Maintained on‑prem servers and supported government weather portal.}
    \resumeItem{Tech: Django, Flask, TCP servers, PostgreSQL, Docker, Python Dash.}
\resumeItemListEnd

\resumeSubheading
{Alem Research}{Jan 2019 -- Jan 2020}
{Software Engineer}{Almaty, KZ}
\resumeItemListStart
    \resumeItem{Designed microservice ETL pipeline for media monitoring using RabbitMQ, Redis, Solr.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Padua}{Oct 2022 -- Jul 2023}
{MSc Mathematics (Algebra \& Geometry)}{Padua, Italy}
\resumeSubheading
{Kazakh-British Technical University}{Aug 2017 -- Jun 2021}
{BSc Applied Mathematics}{Almaty, Kazakhstan}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{Languages: Python (expert), Golang (familiar)}
\resumeItem{Frameworks: Django, DRF, Flask, }
\resumeItem{Databases: PostgreSQL, Redis, MongoDB}
\resumeItem{Tools: Celery, Asyncio, Docker, Git, RabbitMQ, Pytest}
\resumeItem{Other: REST APIs, ETL pipelines, TCP servers, NumPy, pandas}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS & TRAINING.-----------
\section{Certifications \& Training}
\resumeSubHeadingListStart
\resumeItem{Epam Data Engineering Training Program: Databricks, PySpark, ETL pipelines}
\resumeItem{Ozon route256 course: Golang, grpc, microservices, Kafka, concurrency, observability}
\resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
\resumeSubHeadingListStart
\resumeItem{English (C1), Russian (Fluent), Kazakh (B2), Italian (B1)}
\resumeSubHeadingListEnd

\end{document}
